Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-16 paper/paper.tex
update results

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \midrule
    \jsc{} & 4330 & 4330 & 4330 & - & - & - & - \\
    \veight{} & 3404 & 3404 & 3401 & - & - & - & - \\
    \chakra{} & 9104 & 9104 & 9104 & - & - & - & - \\
    \smonkey{} & 3943 & 3943 & 3943 & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[t!]
\setlength{\tabcolsep}{2pt}    
%  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test
    transplantation. Url columns anonymized.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   13 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   16 & 8/08  & V8 & \textbf{Assigned} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \midrule
    \jsc{} & 2278 & - & - & - & - & - & - \\
    \veight{} & 1213 & - & - & - & - & - & - \\
    \chakra{} & 7041 & - & - & - & - & - & - \\
    \smonkey{} & 1761 & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[t!]
\setlength{\tabcolsep}{2pt}    
%  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test
    transplantation. Url columns anonymized.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
   13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   14 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   16 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   17 & 8/08  & V8 & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   18 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table}
